---
title: "Homework: lubridate and purrr"
author: "Carson Cherniss and Ainsley Gallagher"
date: "2025-02-25"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Load Packages: 
```{r loading-packages, message=FALSE, warning=FALSE}
library(tidyverse)
```

## Exercise 1: Advanced date manipulation with lubridate
### Question 1: Generate a sequence of dates from January 1, 2015 to December 31, 2025, spaced by every two months. Extract the year, quarter, and ISO week number for each date.
```{r question 1}
# Generate a sequence of dates from Jan 1, 2015, to Dec 31, 2025, every two months
dates <- seq(ymd("2015-01-01"), ymd("2025-12-31"), by = "2 months")

# Create a tibble and extract year, quarter, and ISO week number
date_tbl <- tibble(
  date = dates,
  year = year(dates),
  quarter = quarter(dates),
  iso_week = isoweek(dates) 
)

print(date_tbl)
```


## Exercise 2: Complex Data Arithmetic
### Question 2: 
```{r question 2}
# R code here
```

## Exercise 3: Higher-Order Functions with purrr
### Question 3: 
```{r question 3}
# R code here
```

## Exercise 4: Combining lubridate and purrr
### Question 4:
```{r question 4}
# R code here
```
